Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2020-02-19 fertile.Rmd
small lit review addition

>>>>

Much of the available literature focuses on file structure, organization, and naming, and `fertile`'s features are consistent with this. The *ideal* file structure is not agreed upon by academics, though there are some recommendations focused on R that are available. *Packaging data analytical work reproducibility using {R} (and friends)* by Marwick, Boettiger, and Mullen provides the framework for file structure that `fertile` is based on: a structure similar to that of an R package, with an `R` folder, as well as `data`, `data-raw`, `inst` and `vignettes`.
